Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-08 Papers/ms.tex
mathbf --> boldsymbol
Started table

\begin{eqnarray}
\left\{
N_{\rm src}, \left\{\mathbf{x}^{\rm src}_i\right\}_{i=1}^N
\right\}
\end{eqnarray}
where $\mathbf{x}^{\rm src}_i$ denotes the parameters for source blob $i$:
\begin{eqnarray}
\mathbf{x}^{\rm src}_i &=& \left\{x_i, y_i, A_i, w_i
\right\}.
\end{eqnarray}

@@

>>>>

\begin{eqnarray}
\left\{
N_{\rm src}, \left\{\boldsymbol{x}^{\rm src}_i\right\}_{i=1}^N
\right\}
\end{eqnarray}
where $\boldsymbol{x}^{\rm src}_i$ denotes the parameters for source blob $i$:
\begin{eqnarray}
\boldsymbol{x}^{\rm src}_i &=& \left\{x_i, y_i, A_i, w_i
\right\}.
\end{eqnarray}

@@

\section{Prior Probability Distributions}
We use the following prior probability distributions:

\begin{table*}
\begin{tabular}{|l|l|l|}
\hline
Quantity	&	Meaning		& Prior\\
\hline
{\bf Hyperparameters}\\
$N_{\rm src}$	&	Number of source blobs	& Uniform($0, 1, ..., 100$)\\
$N_{\rm lens}$	&	Number of lens blobs	& Uniform($0, 1, ..., 10$)\\

{\bf Lens Blob Parameters}\\
{\bf Source Blob Parameters}\\
{\bf Smooth Lens Parameters}\\
{\bf Noise Parameters}\\
{\bf Data}\\
\end{tabular}
\caption{All of the prior distributions.
\label{tab:priors}}
\end{table*}
